|

### 2021-12-07 05-Chp-CPRD-Analysis.Rmd
Fix broken links to appendices

An *a priori* protocol for this study was published,[@walker2016] and amendments to this are recorded in Appendix \@ref(appendix-cprd-amendments).[@vonelm2008]

>>>>

An *a priori* protocol for this study was published,[@walker2016] and amendments to this are recorded in Appendix \@ref(appendix-cprd-amendments).

### 2021-12-07 06-Chp-IPD-Analysis.Rmd
Fix broken links to appendices

Missing values in collected variables was common across the cohorts. A matrix of covariates, and whether they were not available or contained missing values for each included cohort, can be seen Appendix \@ref(hold). The Whitehall II and EPIC cohorts contained data on all but one covariates of interest, while three missing covariates were identified in the CaPS cohort, namely education, BMI and ethnicity. No included cohort provided information on the _ApoE4_ status of participants, and so this variable could not be adjusted for in the analysis.

@@

Across the three cohorts, `r n_total_ipd` participants were included in this analysis (Whitehall II = 8208, EPIC = 1115, CaPS = 2512). All cohorts contained data on the four exposure variables of interest (or sufficient data from which to calculate them) and on all-cause dementia outcomes. The only other dementia outcome examined across cohorts was vascular dementia, which was reported in the CaPS and Whitehall II studies. The definitions of dementia outcomes used across cohorts can be seen in Appendix \@ref(hold). Cumulatively, there were `r n_ipd_dementia` cases of all-cause dementia, with `r n_ipd_vasdem` further classified as vascular dementia. Summary statistics for each cohort are provided in Table \@ref(tab:cohortSummary-table).

>>>>

Missing values in collected variables was common across the cohorts. A matrix of covariates, and whether they were not available or contained missing values for each included cohort, can be seen Appendix \@ref(appendix-ipd-covariate-matrix). The Whitehall II and EPIC cohorts contained data on all but one covariates of interest, while three missing covariates were identified in the CaPS cohort, namely education, BMI and ethnicity. No included cohort provided information on the _ApoE4_ status of participants, and so this variable could not be adjusted for in the analysis.

@@

Across the three cohorts, `r n_total_ipd` participants were included in this analysis (Whitehall II = 8208, EPIC = 1115, CaPS = 2512). All cohorts contained data on the four exposure variables of interest (or sufficient data from which to calculate them) and on all-cause dementia outcomes. The only other dementia outcome examined across cohorts was vascular dementia, which was reported in the CaPS and Whitehall II studies. The definitions of dementia outcomes used across cohorts can be seen in Appendix \@ref(appendix-ipd-dementia-def). Cumulatively, there were `r n_ipd_dementia` cases of all-cause dementia, with `r n_ipd_vasdem` further classified as vascular dementia. Summary statistics for each cohort are provided in Table \@ref(tab:cohortSummary-table).

### 2021-12-07 07-Chp-Triangulation.Rmd
Fix broken links to appendices

Reasonable values for the position and spread of the prior distributions were informed by a previously-reported expert bias elicitation exercise.[@turner2009] Using open data from that study, I calculated the mean values for the mean and variance of the adjustment distributions across all biases considered by that exercise (see Appendix \@ref(?) for more details on how these were calculated). For the purposes of this illustrative analysis and to highlight the generalised nature of the code used to perform the analysis (see Section \@ref(tri-software)), I used the calculated values to inform two scenarios of modifying distributions (Table \@ref(tab:priorsAdd-table)) for additive biases, and a single set for proportional biases. In the first scenario, the relationship between the position assigned to each additive judgement is linear. In the second scenario, the step from "Moderate" to "High" is twice that from "Low" to "Moderate". Across both additive and proportional biases, the variance of the "High" judgement distribution was defined to be greater than that of the "Moderate" judgement.

@@

No substantial differences were observed between the summary estimates obtained under the two scenarios of additive bias (Figure \@ref(fig:fpLdlAdComparison) in Appendix \@ref(appendix-tri-analysis)).

@@

There are two key outputs from this project. The first is the `triangulate` R package. Personal communication with the authors of the original method resulted in the STATA code to implement the bias-/indirectness-adjusted model.[@turner2009] This has since been generalised as part of the `triangulate` R package to enable other users to apply the approach detailed here. The package allows for preprocessing of domain-based risk-of-bias data to correctly identify the direction of the bias relative to the effect estimate, use of domain-specific prior distributions, production of bias direction plots (via the tool described in Appendix \@ref(?), calculation of bias/indirectness-adjusted estimates for each result, and synthesis of these adjusted results in a standard random-effects meta-analysis.

>>>>

Reasonable values for the position and spread of the prior distributions were informed by a previously-reported expert bias elicitation exercise.[@turner2009] Using open data from that study, I calculated the mean values for the mean and variance of the adjustment distributions across all biases considered by that exercise (see Appendix \@ref(appendix-adjustment-values) for more details on how these were calculated). For the purposes of this illustrative analysis and to highlight the generalised nature of the code used to perform the analysis (see Section \@ref(tri-software)), I used the calculated values to inform two scenarios of modifying distributions (Table \@ref(tab:priorsAdd-table)) for additive biases, and a single set for proportional biases. In the first scenario, the relationship between the position assigned to each additive judgement is linear. In the second scenario, the step from "Moderate" to "High" is twice that from "Low" to "Moderate". Across both additive and proportional biases, the variance of the "High" judgement distribution was defined to be greater than that of the "Moderate" judgement.

@@

No substantial differences were observed between the summary estimates obtained under the two scenarios of additive bias (Appendix \@ref(appendix-tri-analysis)).

@@

There are two key outputs from this project. The first is the `triangulate` R package. Personal communication with the authors of the original method resulted in the STATA code to implement the bias-/indirectness-adjusted model.[@turner2009] This has since been generalised as part of the `triangulate` R package to enable other users to apply the approach detailed here. The package allows for preprocessing of domain-based risk-of-bias data to correctly identify the direction of the bias relative to the effect estimate, use of domain-specific prior distributions, production of bias direction plots (via the tool described in Appendix \@ref(appendix-robvis), calculation of bias/indirectness-adjusted estimates for each result, and synthesis of these adjusted results in a standard random-effects meta-analysis.

### 2021-12-07 08-Discussion.Rmd
Fix broken links to appendices

::: {.laybox data-latex=""}
## Lay summary {-}

@@

The aim of this thesis was to attempt to infer the causal effect of blood lipid levels on dementia outcomes. In this discussion, I will review the contribution of each chapter to this central aim, summarise the principal findings and methodological innovations, and discuss the implications of my findings for both clinical and public health practice. I consider the overall strengths and limitations of this thesis as a coherent body of work and suggest avenues for impactful future research that builds on the research presented.

@@

In __Chapter \@ref(sys-rev-tools-heading)__, I introduced the core concepts considered in this thesis and framed the research presented in relation to a theoetical framework of evidence synthesis.

@@

In __Chapter \@ref(sys-rev-methods-heading)__, I describe the methods of a comprehensive systematic review of all available evidence on the association of both lipids and lipid-regulating agents with demetia outcomes. The results of this analysis are then presented in __Chapter \@ref(sys-rev-results-heading)__.

In __Chapter \@ref(cprd-heading)__, I describe an analysis of the association of lipid-regulating agent use and dementia outcomes in the CPRD, a large electronic health record database. I make use of control outcomes to illustrate insufficiently controlled confounding.

In __Chapter \@ref(ipd-heading)__, I present an individual participant data meta-analysis of the association of lipid levels and dementia outcomes, using previously unanalysed data accessed via the Dementia Platform UK.

Finally, in __Chapter \@ref(tri-heading)__, I propose a new method for the systematic integration of multiple evidence sources as part of quantitative triangulation framework. I illustrate the method using two case studies (the effect of LDL-c on Alzheimer's disease and the effect of triglycerides on vascular dementia), drawing on the evidence identified or produced by previous chapters.

@@

Since the searches underpinning the systematic review described in this thesis were performed (July 2019), further studies on this topic have been performed. Two of these, noteable for the analysis of large UK cohorts, are discussed here.

The first is a large-scale analysis of 953,635 patients in the CPRD, followed from their first LDL-c measurement.[@iwagami2021] The study found a slight increased risk of dementia was associated higher LDL-c measured at mid-life, driven by the finding for the Alzheimer's disease subgroup. These findings are consistent with the findings presented in this thesis, particularly given the lack of adjustment for confounding by ApoE4, which was estimated by the study to induce a RR of 1.09 per 1-SD increase in LDL-c in the absence of a true causal effect.

@@

Preprints are an important source of evidence, and searching of preprint repositories should become an accepted part of the evidence synthesis process. To support this, I developed a new tool (as described in Chapter \@ref(sys-rev-tools-heading)) to enable researchers to readily search health-related preprints.

@@

In terms of assessment, I applied domain-based tools to evidence relevant to the effect of lipids on dementia outcomes, and highlighted the limitation of the available tools for Mendelian randomisation studies. I also piloted and provided feedback on a forthcoming tool for assessing the risk of bias due to missing evidence. In the primary analysis of data from the CPRD, I used negative control outcomes to assess the potential for bias due to insufficiently controlled confounding by indication.

@@

Finally, while the framework proposed here could (fairly) be criticised over the validity of the prior distributions of bias/indirectness chosen, the assumptions made about the impact of bias in this thesis are no stronger than those made when synthesising effect estimates as though they were unbiased. The proposed framework at the very least recognises the uncertainty introduced by bias/indirectness, and decreases the precision of the overall effect estimate on this basis.

@@

There are several strengths to this thesis as a whole. Specifically, the identification and triangulation of evidence across study designs and publication status sets this thesis apart from previous synthesis of the evidence on this topic. Additionally, this thesis has also produced new evidence on the association of blood lipids with dementia outcomes in previously unanalysed cohorts, and provided additional information on a previously under-studied association (lipids/LRA and vascular dementia).

A further strength of this thesis is the production of software to support the novel evidence synthesis techniques used. Extensive documentation has been written to guide users through usage of the tools and example data is provided for use. Finally, subtantial effort has been invested to make the research documented in this thesis as reproducible as possible - this is documented more fully in Appendix \@ref(disc-repro-research).

@@

### Weaknessess

However, there are also several strong limitations to this thesis. In the first instance, as with many many studies of dementia outcomes, a limiting factor in the interpretation of the results is the absence of a detailed pathological mechanism. It is possible that statins have a true effect via some other pathway , but without knowledge of the mechanism, the plausibility of this relationship cannot be assessed.

@@

The proposal for the programme of research underpinning this thesis was created in advance of starting my PhD, as a detailed plan was required in order to secure the funding that supported me through my studies. In hindsight, the decision to take a broad approach to the inclusion of dementia outcomes resulted in a larger workload than anticipated, particularly when also considering evidence from multiple different study designs. Additionally, as dementia subtypes likely have very different aetiological pathways, it may have been better to focus on a single subtype (e.g. Alzheimer's disease) when considering the causal effects of lipids. Similarly, attempting to undertake a full individual participant data meta-analysis as a single part of a larger programme of research was overly ambitious, as data cleaning and harmonisation for just three of the many cohorts I applied to was a substantial undertaking.

@@

As noted in Chapter \@ref(sys-rev-results-heading), methods for the inclusion of Mendelian randomisation studies in evidence synthesis exercises are not yet sufficiently developed, particularly in comparison to other study designs. Future work should aim to validate search strategies for this study design, paying particular attention to the range of terms used to define the analytical approach (e.g. genetic instrumental variable analysis). In addition, as discussed in Section \@ref(tri-accuracy), the lack of an established risk-of-bias tool for Mendelian randomisation studies limits subsequent analyses that requires systematic assessment of bias, such as the quantitative triangulation framework proposed here. Creation of a domain-based tool for this study design, which accounts for the differences in potential biases between one- and two-sample approaches, should be considered a priority.

Finally, the inclusion of multiple two-sample Mendelian randomisation studies using identical summary statistics can falsely increase the precision of the summary effect estimate if treated as independent results. Development of best pracice guidance for addressing this problem would represent a useful contribution to the field.

@@

### Systematic reviews and quantiative triangulation

@@

<!-- TODO Could also talk here about how applying it across multiple questions would enable the development of a database of prespecified priors. -->

&nbsp;
<!----------------------------------------------------------------------------->

@@

This thesis has provided new evidence concerning the role of blood lipids as a modifiable risk factor for dementia and highlighted the considerable uncertainty that still remains in relation to this causal question. In addition, it has developed new methods and tools, specifically around the inclusion of preprints in systematic reviews and the quantitative triangulation of evidence sources, which will future evidence synthesists to better address important causal questions.

>>>>

::: {.laybox data-latex=""}
## Lay summary

<!-- TODO Unnumber lay summary -->

@@

The central aim of this thesis was to infer the causal effect of blood lipid levels on dementia outcomes via evidence synthesis methods. In this discussion, I will review the contribution of each chapter to this aim, summarise the principal findings and methodological innovations of the thesis, and discuss the implications of my findings for both clinical and public health practice. I consider the overall strengths and limitations of this thesis as a coherent body of work and suggest avenues for impactful future research that builds on the research presented.

@@

In __Chapter \@ref(sys-rev-tools-heading)__, I introduced the core concepts considered in this thesis and framed the research presented in relation to a theoretical framework of evidence synthesis.

@@

In __Chapter \@ref(sys-rev-methods-heading)__, I described the methods of a comprehensive systematic review of all available evidence on the association of both lipids and lipid-regulating agents with dementia outcomes. The results of this analysis are then presented in __Chapter \@ref(sys-rev-results-heading)__.

In __Chapter \@ref(cprd-heading)__, I described an analysis of the association of lipid-regulating agent use and dementia outcomes in the CPRD, a large electronic health record database. I make use of control outcomes to illustrate insufficiently controlled confounding.

In __Chapter \@ref(ipd-heading)__, I presented an individual participant data meta-analysis of the association of lipid levels and dementia outcomes, using previously unanalysed data accessed via the Dementia Platform UK.

Finally, in __Chapter \@ref(tri-heading)__, I proposed a new method for the systematic integration of multiple evidence sources as part of quantitative triangulation framework. I illustrated the method using two case studies (the effect of LDL-c on Alzheimer's disease and the effect of triglycerides on vascular dementia), drawing on the evidence identified or produced by previous chapters.

@@

Since the searches underpinning the systematic review described in this thesis were performed (July 2019), further studies on this topic have been performed. Two of these, notable for the analysis of large UK cohorts, are discussed here.

The first is a large-scale analysis of 953,635 patients in the CPRD, followed from their first LDL-c measurement.[@iwagami2021] The study found a slight increased risk of dementia was associated higher LDL-c measured at mid-life, driven by the finding for the Alzheimer's disease subgroup. These results are consistent with the findings presented in this thesis, particularly given the lack of adjustment for confounding by ApoE4, which was estimated by the study to induce a RR of 1.09 per 1-SD increase in LDL-c in the absence of a true causal effect.

@@

Preprints are an important source of evidence and searching of preprint repositories should become an accepted part of the evidence synthesis process. To support this, I developed a new tool (as described in Chapter \@ref(sys-rev-tools-heading)) to enable researchers to readily search health-related preprints.

@@

In terms of assessment, I applied domain-based tools to evidence relevant to the effect of lipids on dementia outcomes and highlighted the limitation of the available tools for Mendelian randomisation studies. I also piloted and provided feedback on a forthcoming tool for assessing the risk of bias due to missing evidence. In the primary analysis of data from the CPRD, I used negative control outcomes to assess the potential for bias due to insufficiently controlled confounding by indication.

@@

Finally, while the framework proposed here could (fairly) be criticised over the validity of the prior distributions of bias/indirectness chosen, the assumptions made about the impact of bias in this thesis are no stronger than those made when synthesising effect estimates as though they were unbiased. The proposed framework at the very least recognises the uncertainty introduced by bias/indirectness and decreases the precision of the overall effect estimate on this basis.

@@

There are several strengths to this thesis as a whole. Specifically, the identification and triangulation of evidence across study designs and publication status sets this thesis apart from previous synthesis of the evidence on this topic. Additionally, this thesis has also produced new evidence on the association of blood lipids with dementia outcomes in previously unanalysed cohorts and provided additional information on a previously under-studied association (lipids/LRA and vascular dementia).

A further strength of this thesis is the production of software to support the novel evidence synthesis techniques used. Extensive documentation has been written to guide users through usage of the tools and example data is provided for use. Finally, substantial effort has been invested to make the research documented in this thesis as reproducible as possible - this is documented more fully in Appendix \@ref(disc-repro-research).

@@

### Weaknesses

However, there are also several strong limitations to this thesis. In the first instance, as with many studies of dementia outcomes, a limiting factor in the interpretation of the results is the absence of a detailed pathological mechanism. It is possible that statins have a true effect via some other pathway , but without knowledge of the mechanism, the plausibility of this relationship cannot be assessed.

@@

The proposal for the program of research underpinning this thesis was created in advance of starting my PhD, as a detailed plan was required in order to secure the funding that supported me through my studies. In hindsight, the decision to take a broad approach to the inclusion of dementia outcomes resulted in a larger workload than anticipated, particularly when also considering evidence from multiple different study designs. Additionally, as dementia subtypes likely have very different aetiological pathways, it may have been better to focus on a single subtype (e.g. Alzheimer's disease) when considering the causal effects of lipids. Similarly, attempting to undertake a full individual participant data meta-analysis as a single part of a larger program of research was overly ambitious, as data cleaning and harmonisation for just three cohorts was a substantial undertaking.

@@

As noted in Chapter \@ref(sys-rev-results-heading), methods for the inclusion of Mendelian randomisation studies in evidence synthesis exercises are not yet sufficiently developed, particularly in comparison to other study designs. Future work should aim to validate search strategies for this study design, paying particular attention to the range of terms used to define the analytical approach (e.g. genetic instrumental variable analysis). In addition, as discussed in Section \@ref(tri-accuracy), the lack of an established risk-of-bias tool for Mendelian randomisation studies limits subsequent analyses that requires systematic assessment of bias, such as the quantitative triangulation framework proposed here. Creation of a domain-based tool for this study design, which accounts for the differences in potential biases between one- and two-sample approaches, should be considered a priority. 
Finally, the inclusion of multiple two-sample Mendelian randomisation studies using identical summary statistics can falsely increase the precision of the summary effect estimate if treated as independent results. Development of best practice guidance for addressing this problem would represent a useful contribution to the field.

@@

### Systematic reviews and quantitative triangulation

@@

<!-- TODO Could also talk here about how applying it across multiple questions would enable the development of a database of prespecified priors. -->
&nbsp;
<!----------------------------------------------------------------------------->

@@

To conclude, this thesis has provided new evidence concerning the role of blood lipids as a modifiable risk factor for dementia and highlighted the considerable uncertainty that still remains in relation to this causal question. In addition, it has developed new methods and tools, specifically around the inclusion of preprints in systematic reviews and the quantitative triangulation of evidence sources, which will enable future evidence synthesists to better address important causal questions.

### 2021-12-07 front-and-back-matter/99-appendices.Rmd
Fix broken links to appendices

---
output:
  pdf_document: default
  html_document: default
---
`r if(knitr:::is_latex_output()) '\\startappendices'`

@@

<!-- If you feel it necessary to include an appendix, it goes here. The first appendix should include the commands above. -->

@@

<!----------------------------------------------------------------------------->
# Appendices by Chapter {#chapter-appendix-heading}

&nbsp;

@@

<!----------------------------------------------------------------------------->
## Chapter \@ref(background-heading) {#appendix-into}

<!----------------------------------------------------------------------------->
### Publications beyond the scope of this thesis {#appendix-publications}

@@

<!----------------------------------------------------------------------------->

@@

<!----------------------------------------------------------------------------->

## Chapter \@ref(sys-rev-tools-heading) {#appendix-sys-rev-tools}
<!----------------------------------------------------------------------------->

@@

## Chapter \@ref(sys-rev-methods-heading) {#appendix-sys-rev}
<!----------------------------------------------------------------------------->

@@

@@

&nbsp;

<!----------------------------------------------------------------------------->
(ref:searchHits-caption) Overview of the full Medline search strategy.

@@

<!----------------------------------------------------------------------------->

&nbsp;

&nbsp;

<!----------------------------------------------------------------------------->
(ref:wosDatabases-caption) Summary of Web of Science databases searched.

```{r wosDatabases-table, message=FALSE, results="asis", echo = FALSE}

```
<!----------------------------------------------------------------------------->

&nbsp;

<!----------------------------------------------------------------------------->
### Code to search preprints {#appendix-medrxivr-code}

@@

### Calculating Gwet's AC1

@@

<!----------------------------------------------------------------------------->
### MR risk of bias tool {#appendix-mr-rob}

<!----------------------------------------------------------------------------->
(ref:mrTool-caption) Tool used to assess risk of bias in Mendelian randomisation studies, adapted from that developed by Mamluk et al.[@mamluk2020]

@@

### Dose response plots by fraction

<!----------------------------------------------------------------------------->
(ref:drDemeniaTC-cap) Dose-response meta-analysis of total cholesterol on all-cause dementia

@@

```{r drDemeniaTC, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:drDemeniaTC-cap)', out.width='100%', fig.scap='(ref:drDemeniaTC-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/dr_Dementia_TC.png"))
```
<!----------------------------------------------------------------------------->

<!----------------------------------------------------------------------------->
(ref:drAdLDL-cap) Dose-response meta-analysis of low-density lipoprotein cholesterol on Alzheimer's disease

@@

```{r drAdLDL, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:drAdLDL-cap)', out.width='100%', fig.scap='(ref:drAdLDL-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/dr_AD_LDL.png"))
```
<!----------------------------------------------------------------------------->

<!----------------------------------------------------------------------------->
## Chapter \@ref(cprd-analysis-heading) {#appendix-cprd-analysis}
<!----------------------------------------------------------------------------->

@@

@@

## Chapter \@ref(ipd-heading) {#appendix-ipd-analysis}
<!----------------------------------------------------------------------------->
### Email and documents sent to potental collaborators {#ipd-email-collab}

<!----------------------------------------------------------------------------->
## Chapter \@ref(tri-heading) {#appendix-tri-analysis}
<!----------------------------------------------------------------------------->
### Calculation of average adjustment from expert elicitation

<!----------------------------------------------------------------------------->
### Code lists

<!----------------------------------------------------------------------------->
### Comparison of two scenarios of bias

<!----------------------------------------------------------------------------->
(ref:fpLdlAdComparison-cap) Comparison of bias-/indirectness-adjusted meta-analyses of LDL-c/Alzheimer's disease, using two different scenarios for the relationship of levels of bias. The left forest plot shows the result where the difference in mean value between the "High" and "Moderate" bias levels is the same as between the "Moderate" and "Low" levels. In the right plot, the difference in mean value between "High" and "Moderate" is twice that between "Moderate" and "Low".

@@

```{r fpLdlAdComparison, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:fpLdlAdComparison-cap)', out.width='100%', fig.scap='(ref:fpLdlAdComparison-scap)'}
knitr::include_graphics(file.path("figures/tri/fp_paired_midlife_ldl_ad_scenarios.png"))
```
<!----------------------------------------------------------------------------->

<!----------------------------------------------------------------------------->
(ref:fpTgVaDComparison-cap) Comparison of bias-/indirectness-adjusted meta-analyses of triglycerides/vascular dementia, using two different scenarios for the relationship of levels of bias. The left forest plot shows the result where the difference in mean value between the "High" and "Moderate" bias levels is the same as between the "Moderate" and "Low" levels. In the right plot, the difference in mean value between "High" and "Moderate" is twice that between "Moderate" and "Low".

@@

```{r fpTgVaDComparison, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:fpTgVaDComparison-cap)', out.width='100%', fig.scap='(ref:fpTgVaDComparison-scap)'}
knitr::include_graphics(file.path("figures/tri/fp_paired_midlife_tg_vad_scenarios.png"))
```
<!----------------------------------------------------------------------------->

<!----------------------------------------------------------------------------->
## Chapter \@ref(discussion-heading)

@@

<!----------------------------------------------------------------------------->
### Catalogue of failures {#appendix-catalogue-failures}

@@

<!----------------------------------------------------------------------------->
# Other Appendices {#other-appendix-heading}

@@

<!----------------------------------------------------------------------------->
## Producing risk-of-bias visualisations with `robvis` {#appendix-robvis}

>>>>

`r if(knitr:::is_latex_output()) '\\startappendices'`

@@

@@

# Appendices by Chapter {#chapter-appendix-heading}

@@

## Chapter \@ref(background-heading) {#appendix-into}

### Publications beyond the scope of this thesis {#appendix-publications}

@@

@@

## Chapter \@ref(sys-rev-tools-heading) {#appendix-sys-rev-tools}

@@

## Chapter \@ref(sys-rev-methods-heading) {#appendix-sys-rev}

@@

(ref:wosDatabases-caption) Summary of Web of Science databases searched.

```{r wosDatabases-table, message=FALSE, results="asis", echo = FALSE}
```

&nbsp;<!----------------------------------------------------------------------->

@@

(ref:searchHits-caption) Overview of the full Medline search strategy.

@@

&nbsp;<!----------------------------------------------------------------------->

### Code to search preprints {#appendix-medrxivr-code}

@@

### Calculating Gwet's AC1 {#appendix-gwet}

@@

### MR risk of bias tool {#appendix-mr-rob}

(ref:mrTool-caption) Tool used to assess risk of bias in Mendelian randomisation studies, adapted from that developed by Mamluk et al.[@mamluk2020]

@@

### Dose response plots by fraction {#appendix-dr-fraction}

(ref:drDemeniaTC-cap) Dose-response meta-analysis of total cholesterol on all-cause dementia

@@

```{r drDemeniaTC, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:drDemeniaTC-cap)', out.width='100%', fig.scap='(ref:drDemeniaTC-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/dr_Dementia_TC.png"))
```

(ref:drAdLDL-cap) Dose-response meta-analysis of low-density lipoprotein cholesterol on Alzheimer's disease

@@

```{r drAdLDL, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:drAdLDL-cap)', out.width='100%', fig.scap='(ref:drAdLDL-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/dr_AD_LDL.png"))
```

## Chapter \@ref(cprd-analysis-heading) {#appendix-cprd-analysis}

@@

## Chapter \@ref(ipd-heading) {#appendix-ipd-analysis}

### Email and documents sent to potental collaborators {#ipd-email-collab}

### Covariate matrix {#appendix-ipd-covariate-matrix}

### Dementia definitions across cohorts {#appendix-ipd-dementia-def}

&nbsp;<!----------------------------------------------------------------------->

## Chapter \@ref(tri-heading) {#appendix-tri-analysis}

### Calculation of average adjustment from expert elicitation {#appendix-adjustment-values}

@@

### Comparison of two scenarios of bias

(ref:fpLdlAdComparison-cap) Comparison of bias-/indirectness-adjusted meta-analyses of LDL-c/Alzheimer's disease, using two different scenarios for the relationship of levels of bias. The left forest plot shows the result where the difference in mean value between the "High" and "Moderate" bias levels is the same as between the "Moderate" and "Low" levels. In the right plot, the difference in mean value between "High" and "Moderate" is twice that between "Moderate" and "Low".

@@

```{r fpLdlAdComparison, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:fpLdlAdComparison-cap)', out.width='100%', fig.scap='(ref:fpLdlAdComparison-scap)'}
knitr::include_graphics(file.path("figures/tri/fp_paired_midlife_ldl_ad_scenarios.png"))
```

(ref:fpTgVaDComparison-cap) Comparison of bias-/indirectness-adjusted meta-analyses of triglycerides/vascular dementia, using two different scenarios for the relationship of levels of bias. The left forest plot shows the result where the difference in mean value between the "High" and "Moderate" bias levels is the same as between the "Moderate" and "Low" levels. In the right plot, the difference in mean value between "High" and "Moderate" is twice that between "Moderate" and "Low".

@@

```{r fpTgVaDComparison, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:fpTgVaDComparison-cap)', out.width='100%', fig.scap='(ref:fpTgVaDComparison-scap)'}
knitr::include_graphics(file.path("figures/tri/fp_paired_midlife_tg_vad_scenarios.png"))
```

## Chapter \@ref(discussion-heading)

@@

### Catalogue of failures {#appendix-catalogue-failures}

@@

# Other Appendices {#other-appendix-heading}

@@

## Producing risk-of-bias visualisations with `robvis` {#appendix-robvis}
